Simulation of seed dispersal distance

### 2020-10-05 appendixB/appendixB.Rmd
Creating markdown to show results of seed dispersal

```{r loadPackages}
library(tidyverse)
library(lubridate)
library(ggpubr)
```

```{r importData}
seed_data_popind <- readRDS("appendixA/seed_dispersal_popind.RDS") %>% 
  mutate(type = ifelse(data == "pop", "population", "individual"))

mixed_ind <- readRDS("appendixA/mixed_ind_seed.RDS")

seed_data_popfam <- readRDS("appendixA/seed_dispersal_popfam.RDS") %>% 
  mutate(type = ifelse(data == "pop", "population", "family"))

mixed_fam <- readRDS("appendixA/mixed_fam_seed.RDS")

@@

```{r eval = FALSE}
# Get all the seed distance data into a single data frame

mixed_mod %>%  
  ungroup() %>% 
  dplyr::select(dispersal, IC) %>%
  mutate(model = "mixed",
         type = str_to_lower(IC)) %>% 
  dplyr::select(model, dispersal, type) -> mixed_data

get_all <- rbind.data.frame(all_seed_data, mixed_data)
saveRDS(get_all, "output/get_all.RDS")

```{r}

all_ind <- rbind.data.frame(seed_data_popind, mixed_ind)
#seed_data_popind %>% 
all_ind %>% ggplot(., aes(x = model, y = dispersal, color = type)) +
  geom_boxplot() +
  theme_bw()
```

Get the ldd for the initial models:
```{r}
# how many LDD events for each model for pop or individual

#seed_data_popind %>% 
  all_ind %>% 
  dplyr::filter(dispersal >= 500) %>% 
  mutate(dispersal = 1) %>% 
  group_by(., , model) %>% 
  summarise(nLDD_events = sum(dispersal)) %>% 
  knitr::kable()
```

Summarize some values for these distances:

```{r}
#seed_data_popind %>% 
  all_ind %>% 
  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
         movement_model = paste(str_replace(model, "_move", ""), 
                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
move_model %>% 
  group_by(movement_model) %>% 
  summarise(LDD = sum(ldd),
            prcnt_ldd = 100*mean(ldd),
            avg = mean(dispersal),
            median = median(dispersal),
            max = max(dispersal)) %>% 
  arrange(prcnt_ldd) %>% 
  knitr::kable()
```

Keep in mind that the figure only goes to 2000, when the max for lognormal movement models is close to 9000, it really sends the estimates far far. 
```{r fig.width=12, fig.height=6}
move_model %>% 
  #filter(model != "lnorm_move") %>% 
  ggplot(., aes(x = dispersal, color = movement_model)) + 
  geom_line(stat = "density") +
  theme_bw()
```

# Family level

```{r}
all_fam <- rbind.data.frame(seed_data_popfam, mixed_fam)

```{r}
all_fam %>% 
  ggplot(., aes(x = model, y = dispersal, color = type)) +
  geom_boxplot() +
  #geom_boxplot(data = mixed_fam, aes(x = type, y = dispersal)) +
  theme_bw()

Get the ldd for the initial models:
```{r}
# how many LDD events for each model for pop or individual

all_fam %>% 
  dplyr::filter(dispersal >= 500) %>% 
  mutate(dispersal = 1) %>% 
  group_by(., , model) %>% 
  summarise(nLDD_events = sum(dispersal)) %>% 
  knitr::kable()
```

Summarize some values for these distances:

```{r}
all_fam %>% 
  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
         movement_model = paste(str_replace(model, "_move", ""), 
                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
move_model %>% 
  group_by(movement_model) %>% 
  summarise(LDD = sum(ldd),
            prcnt_ldd = 100*mean(ldd),
            avg = mean(dispersal),
            median = median(dispersal),
            max = max(dispersal)) %>% 
  arrange(prcnt_ldd) %>% 
  knitr::kable()
```

Keep in mind that the figure only goes to 2000, when the max for lognormal movement models is close to 9000, it really sends the estimates far far. 
```{r fig.width=12, fig.height=6}
move_model %>% 
  #filter(model != "lnorm_move") %>% 
  ggplot(., aes(x = dispersal, color = movement_model)) + 
  geom_line(stat = "density") +
  theme_bw()
```

>>>>

```{r loadPackages}
library(tidyverse)
library(lubridate)
library(cowplot)
```

```{r importData}
seed_data_popind <- readRDS("appendixA/seed_dispersal_popind.RDS")

seed_data_popfam <- readRDS("appendixA/seed_dispersal_popfam.RDS")

@@
